The French Covid-19 vaccination policy did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals

### 2022-07-04 ms/figs.Rmd
format output table OR

# Extract only key columns
tmp <- outLR[, c("varPred", "typePredFull", "thedate", "OR", "OR.CI.min", "OR.CI.max")]
# Rename the columns
names(tmp) <- c("predictor", "class of predictor", "date", "OR", "OR CI min", "OR CI max")

>>>>

# Extract only key columns
tmp <- outLR[, c("varPred", "typePredFull", "thedate", "OR", "OR.CI.min", "OR.CI.max")]
# Remove the lines corresponding to permutations
tmp <- tmp[tmp$permutation == FALSE, ]
# Rename the columns
names(tmp) <- c("predictor", "class of predictor", "date", "OR", "OR CI min", "OR CI max")
